Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-05-30 EMNLP-demo-paper/conclusion.tex
update intro

Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
%
In the future, we plan to improve upon the current attention interface and expand the visualization component further to handle tasks such neural machine translation and more.

>>>>

Even though we design the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open source package, and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-30 EMNLP-demo-paper/intro.tex
update intro

To address these challenges in interpreting attention-based models, 
we introduce a flexible Python library that allows the user to easily generate a web-based interactive visual analytics environment for various usage via a composable visualization component design.
%
To facilitate exploratory analysis (see Figure~\ref{fig:modelPipeline}), we employ a fully interactive pipeline, in which the user can perturb the input text (via two perturbation schemes discussed in Section~\ref{sec:perturb}) and observe the effects on the attention and prediction, or modify the attention to understand how it affects predictions.
%
Finally, we demonstrate our system on two primary NLP tasks: natural language
inference (NLI) and machine comprehension (MC). 
%For the NLI task, we visualize
%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
%For the MC task, we present your visualization methods on bidirectional attention flow model,
%which also represents a line of state-of-the-art models \cite{Seo2016}.

@@

>>>>

@@

To address these challenges in interpreting attention-based models, 
we introduce a python library that allows users to create web-based interactive visual analytics environments,
in which they can interrogate the model by perturbing the input text and observing the effects on the attention and prediction, or modifying the attention and studying how it affects predictions (see Figure~\ref{fig:modelPipeline}).
%
We demonstrate our system on two primary NLP tasks: natural language
inference (NLI) and machine comprehension (MC). 
%For the NLI task, we visualize
%decomposable attention networks which represents a series of strongly performing models \cite{Parikh2016}.
%For the MC task, we present your visualization methods on bidirectional attention flow model,
%which also represents a line of state-of-the-art models \cite{Seo2016}.
